### 2018-06-25 pubs/itp-2018/sections/metis-language-and-proofs.tex
Add the current output from athena for the article's problem

\begin{figure}
\begin{Verbatim}[commandchars=\\\{\}, numbers=left,xleftmargin=5mm]
fof(premise, axiom, (p ⇒ q) ∧ (q ⇒ p)).  \label{line1}
fof(goal, conjecture, (p ∨ q) ⇒ (p ∧ q)).  \label{line2}
fof(s₀, (p ∨ q) ⇒ p, inf(strip, goal)).  \label{line3}
fof(s₁, ((p ∨ q) ∧ p) ⇒ q, inf(strip, goal)).  \label{line4}
fof(neg₀, ¬ ((p ∨ q) ⇒ p), inf(negate, s₀)).  \label{line5}
fof(n₀₀, (¬ p ∨ q) ∧ (¬ q ∨ p), inf(canonicalize, premise)).  \label{line6}
fof(n₀₁, ¬ q ∨ p, inf(conjunct, n₀₀)).  \label{line7}
fof(n₀₂, ¬ p ∧ (p ∨ q), inf(canonicalize, neg₀)).  \label{line8}
fof(n₀₃, p ∨ q, inf(conjunct, n₀₂)).  \label{line9}
fof(n₀₄, ¬ p, inf(conjunct, n₀₂)).  \label{line10}
fof(n₀₅, q, inf(simplify, [n₀₃, n₀₄])).  \label{line11}
cnf(r₀₀, ¬ q ∨ p, inf(canonicalize, n₀₁)).  \label{line12}
cnf(r₀₁, q, inf(canonicalize, n₀₅)).  \label{line13}
cnf(r₀₂, p, inf(resolve, q, [r₀₁, r₀₀])).  \label{line14}
cnf(r₀₃, ¬ p, inf(canonicalize, n₀₄)).  \label{line15}
cnf(r₀₄, ⊥, inf(resolve, p, [r₀₂, r₀₃])).  \label{line16}
fof(neg₁, ¬ ((p ∨ q) ∧ p) ⇒ q, inf(negate, s₁)).  \label{line17}
fof(n₁₀, ¬ q ∧ p ∧ (p ∨ q), inf(canonicalize, neg₁)).  \label{line18}
fof(n₁₁, (¬ p ∨ q) ∧ (¬ q ∨ p), inf(canonicalize, premise)).  \label{line19}
fof(n₁₂, ¬ p ∨ q, inf(conjunct, n₁₁)).  \label{line20}
fof(n₁₃, ⊥, inf(simplify,[n₁₀, n₁₂])).  \label{line21}
cnf(r₁₀, ⊥, inf(canonicalize, n₁₃)).  \label{line22}
\end{Verbatim}
\caption{Customized \Metis \TSTP derivation of the theorem in~\eqref{eq:complete-example-problem}.}
\label{complete-metis-example}
\end{figure}

>>>>

\input{sections/data/problem.tstp.tex}
